%-------------------------
% Resume in Latex
% Author : Vichita Fongmala
% License : MIT
%------------------------

\documentclass[letterpaper,12pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/vfongmala/}{\Large Vichita Fongmala}} & Email : \href{mailto:vichita.f@gmail.com}{vichita.f@gmail.com}\\
  \href{https://www.linkedin.com/in/vfongmala/}{linkedin.com/in/vfongmala/} & Mobile : +61415324853 \\
\end{tabular*}


%-----------EXPERIENCE-----------------
\section{Experience: 10+ years on Android development}
  \resumeSubHeadingListStart

    \resumeSubheading
    {SafetyCulture}{Sydney, Australia}
    {Senior Software Engineer}{Jun. 2022 - Present}
    \resumeItemListStart
      \resumeItem{SafetyCulture Application}
        {Developing features of application. Leading the team in the ``Folder on mobile" feature development. Integrating Android application with external bluetooth devices. Including A/B testing, unit testing, integration testing, data tracking, and release an application.}
      \resumeItem{Project Leading}
        {Leading the team in building the new tool to improve engineering productivity.}
    \resumeItemListEnd

    \resumeSubheading
      {Willow Inc.}{Sydney, Australia (Remote)}
      {Senior Software Engineer}{Mar. 2021 - Mar. 2022}
      \resumeItemListStart
        \resumeItem{Willow Rail}
          {Developing features of application. Implementing automation test from the ground up and integrated into Azure DevOps pipeline for both Android and iOS.}
        \resumeItem{Insite}
          {Developing features of application. Including unit testing and release an application.}
      \resumeItemListEnd

    \resumeSubheading
      {Agoda}{Bangkok, Thailand}
      {Senior Software Engineer}{Feb. 2020 - Mar. 2021}
      \resumeItemListStart
        \resumeItem{Release Management Tool}
          {Developing an automation system to override human tasks related to releasing the applications to store for both Android and iOS.}
        \resumeItem{Agoda Application}
          {Developing features of application. Including A/B testing, unit testing, integration testing, data tracking, and release an application.}
        \resumeItem{Onboarding buddy}
          {Guiding and helping new joiner during onboarding process.}
      \resumeItemListEnd

    \resumeSubSubheading
      {Mobile Software Developer}{Mar. 2015 - Feb. 2020}
      \resumeItemListStart
        \resumeItem{Agoda Application}
          {Developing features of application. Including A/B testing, unit testing, integration testing, data tracking, and release an application.}
        \resumeItem{Onboarding buddy}
          {Guiding and helping new joiner during onboarding process.}

      \resumeItemListEnd

    \resumeSubheading
      {MagicBox Asia}{Bangkok, Thailand}
      {Android Developer}{Jan. 2014 - Feb. 2015}
      \resumeItemListStart
        \resumeItem{MagicBox SDK}
          {Developing a SDK for embedding member systems into existing mobile games.}
        \resumeItem{Mobile Game Localization}
          {Localizing foreign mobile games for into Thai locale. Config using Cocos2d-x framework, build, and release mobile games.}
      \resumeItemListEnd

    \resumeSubheading
      {AppMan}{Bangkok, Thailand}
      {Mobile Application Developer}{Aug. 2013 - Dec 2013}
      \resumeItemListStart
        \resumeItem{Dating Application}
          {Developing an application which match users from their interests and create chat room to start conversation.}
        \resumeItem{Insurance Application}
          {Developing an application for insurance agent. Allow customer to fill and submit the insurance form within application without using paper.}
      \resumeItemListEnd

    \resumeSubheading
      {Freelancer}{Bangkok, Thailand}
      {Android Developer}{2014 - Present}
      \resumeItemListStart
        \resumeItem{Thai Citizen Rights}
          {Developing an informative application for Thai citizen's rights. Show list categorized by type of citizens. Show government sector locations on map.}
        \resumeItem{Smart Piggy Bank}
          {Developing an application which sync with physical piggy bank via bluetooth to update amount of money in piggy bank.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: Kotlin, Java, C\#, C++, Swift}
    }
    \item{
      \textbf{Android Technologies}{: Koin, Dagger, Jetpack Compose, Coroutines, RxJava, Retrofit, JUnit, Espresso, MVVM, MVP, Play Store Publish}
    }
    \item{
      \textbf{Other Technologies}{: CI/CD (Azure DevOps, TeamCity, Buildkite, CircleCI), Firebase, Microsoft AppCenter, Git, Appium, iOS, RESTful API, Docker, .NET MAUI, BPMN, Agile}
    }
  \resumeSubHeadingListEnd


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {KMUTT}{Bangkok, Thailand}
      {Bachelor of Science in Computer Science;  GPA: 3.53}{May. 2009 -- Feb. 2013}
    \resumeSubheading
      {Inje University}{Gimhae, South Korea}
      {Exchange study on Computer Engineer}{Mar. 2013 -- June. 2013}
  \resumeSubHeadingListEnd

%-------------------------------------------

\end{document}
